Manuscript Figures for Genome Biology

### 2018-06-06 manuscript_figures/manuscript_figures.Rmd
Fix code order in alt supplementary figure

## create table of total tests for each case study
objdat_tab <- dplyr::select(objdat_props, casestudy, nrejects, propPossible, assay)
objdat_tab <- dplyr::distinct(objdat_tab)
objdat_tab <- dplyr::mutate(objdat_tab, `Total Tests` = scales::comma(round(nrejects / propPossible)))

@@

## specify method order
method_order <- c("bonf", "bh", "ihw", "qvalue", "bl", "lfdr",
                  "scott-empirical", "scott-theoretical", "ashq")
objdat_joint <- dplyr::mutate(objdat_joint, method = factor(method, levels = c(method_order, "Total Tests")))

## create table of rejected proportion for top methods per case study
objdat_props <- dplyr::group_by(objdat, casestudy)
objdat_props <- dplyr::filter(objdat_props, nrejects == max(nrejects, na.rm = TRUE))
objdat_props <- dplyr::ungroup(objdat_props)
objdat_props <- dplyr::mutate(objdat_props,
                              lab = paste0(nrejects, "\n(", 100*round(propPossible, 4), "%)"))
objdat_props$plotrow <- "real"
```

>>>>

## create table of rejected proportion for top methods per case study
objdat_props <- dplyr::group_by(objdat, casestudy)
objdat_props <- dplyr::filter(objdat_props, nrejects == max(nrejects, na.rm = TRUE))
objdat_props <- dplyr::ungroup(objdat_props)
objdat_props <- dplyr::mutate(objdat_props, lab = paste0(100*round(propPossible, 4), "%"))
objdat_props$plotrow <- "real"

## create table of total tests for each case study
objdat_tab <- dplyr::select(objdat_props, casestudy, nrejects, propPossible, assay)
objdat_tab <- dplyr::distinct(objdat_tab)
objdat_tab <- dplyr::mutate(objdat_tab, `Total Tests` = scales::comma(round(nrejects / propPossible)))
objdat_tab <- dplyr::select(objdat_tab, casestudy, assay, `Total Tests`) 
objdat_tab <- tidyr::gather(objdat_tab, method, cnt, -casestudy, -assay)

@@

## specify method order
method_order <- c("bonf", "bh", "ihw", "qvalue", "bl", "lfdr",
                  "scott-empirical", "scott-theoretical", "ashq")
objdat_joint <- dplyr::mutate(objdat_joint, method = factor(method, levels = c(method_order, "Total Tests")))
```
